### 2016-12-23 Chapters/theory.tex
minor correction in theory.tex. Version of intro and discussion sent to Hidde and Hans

\textit{Rather than propose a new theory or unearth a new fact, often the most important contribution a scientist can make is to discover a new way of seeing old theories or facts.} -- Richard Dawkins, \textit{The Selfish Gene}, preface to 1989 edition.

@@

Analysis of the nondimensionalized system allows a number of properties of the solution of the optimal control problem of Eq.~\ref{eq:J} to be derived (\textit{Methods} and \ref{S3_Text}).
First, by applying a version of the well-known Pontryagin Maximum Principle \cite{carlson_infinite_1991}, we can prove that the optimal solution is obtained for an alternating sequence of $\alpha(\cdot)=0$ and $\alpha(\cdot)=1$, possibly ending with an intermediate value of $\alpha(\cdot)$, corresponding to the optimal steady state $(\hat{p}(t),\hat{r}(t))=(\hat{p}_{opt}^*,\hat{r}_{opt}^*)$, that is, the steady state leading to the optimal growth rate $\hat{\mu}_{opt}^*$ in the post-upshift environment $E_M$.
Second, if the optimal solution reaches the optimal steady state for the new environment, then it does so after an infinite number of switches of $\alpha (\cdot)$ between 0 and 1.
Third, this switching behavior is characterized by a so-called switching curve $\hat{r}=\varphi(\hat{p})$ in the $(\hat{p},\hat{r})$-plane, which passes through $(\hat{p}_{opt}^*,\hat{r}_{opt}^*)$.
The switching curve divides the phase plane into two regions, such that $\alpha(\cdot)$ switches to 0 when the system is in the region above $\varphi$ and to 1 when the system is below $\varphi$ (black dashed curve in Fig.~\ref{fig:optimalcontrol}\textit{A}).

>>>>

\textit{Rather than propose a new theory or unearth a new fact, often the most important contribution a scientist can make is to discover a new way of seeing old theories or facts.} -- Richard Dawkins, \textit{The Selfish Gene}~\cite{dawkins_selfish_1976}, preface to 1989 edition.

@@

Analysis of the nondimensionalized system allows a number of properties of the solution of the optimal control problem of Eq.~\ref{eq:J} to be derived (\textit{Methods} and \ref{S3_Text}).
First, by applying a version of the well-known Pontryagin Maximum Principlek~\cite{carlson_infinite_1991}, we can prove that the optimal solution is obtained for an alternating sequence of $\alpha(\cdot)=0$ and $\alpha(\cdot)=1$, possibly ending with an intermediate value of $\alpha(\cdot)$, corresponding to the optimal steady state $(\hat{p}(t),\hat{r}(t))=(\hat{p}_{opt}^*,\hat{r}_{opt}^*)$, that is, the steady state leading to the optimal growth rate $\hat{\mu}_{opt}^*$ in the post-upshift environment $E_M$.
Second, if the optimal solution reaches the optimal steady state for the new environment, then it does so after an infinite number of switches of $\alpha (\cdot)$ between 0 and 1.
Third, this switching behavior is characterized by a so-called switching curve $\hat{r}=\varphi(\hat{p})$ in the $(\hat{p},\hat{r})$-plane, which passes through $(\hat{p}_{opt}^*,\hat{r}_{opt}^*)$.
The switching curve divides the phase plane into two regions, such that $\alpha(\cdot)$ switches to 0 when the system is in the region above $\varphi$ and to 1 when the system is below $\varphi$ (black dashed curve in Fig.~\ref{fig:optimalcontrol}\textit{A}).
